A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-03-22 JTB_ms/JTB_ms.tex
remake w fixed ss oscill filter

Prey uptake rate

@@

mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}

@@

Specific maintenance rate of host biomass

@@

Specific maintenance rate of symbiont biomass

@@

Proportion host N-turnover recycled to host

@@

Proportion host C-turnover recycled to photosynthesis

@@

Proportion symbiont N-turnover recycled to symbiont

@@

Proportion symbiont C-turnover recycled to photosynthesis

@@

Maximum specific assimilation rate from host feeding

@@

Half-saturation constant for prey uptake by host

@@

Maximum specific DIN uptake rate by host

@@

Half-saturation constant for DIN uptake by host

@@

Efficacy of CO\textsubscript{2} delivery by host CCMs

@@

This flux, \(j_{eC}\), is assumed to be available to the host as a
respiratory substrate to support energetically-demanding processes; of
particular importance is the host's active carbon concentrating
mechanisms (CCMs) that supply CO\textsubscript{2} for symbiont
photosynthesis (Wooldridge 2013; Hopkinson, Tansik, and Fitt 2015). We
therefore specify \(j_{CO_2}\) as the host-mediated delivery of
CO\textsubscript{2} to photosynthesis that encompasses potentially
diverse carbon-concentrating mechanisms (CCMs), including active
transport of bicarbonate, carbonic anhydrase-catalyzed conversion of
bicarbonate to CO\textsubscript{2} to promote diffusion toward the
symbiont (Tansik, Fitt, and Hopkinson 2015), and acidification of the
symbiosome to increase localized CO\textsubscript{2} concentrations
around the symbiont (Barott et al. 2014). Since these active CCMs
require energetic input by the host, we define \(j_{CO_2}\) as
proportional to \(j_{eC}\), assuming that some of this carbon is
respired to energize the CCMs. This formulation means that the symbiont
indirectly ensures its own CO\textsubscript{2} supply by providing fixed
carbon (=energy) to the host (Wooldridge 2013). The parameter
\(k_{CO_2}\) scales the efficacy of host CCMs, which enables the
comparison of different rates of CO\textsubscript{2} delivery that may
characterize different coral species (Wooldridge 2014a). The active
input of CO\textsubscript{2} to the photosynthesis SU is therefore
specified as:

>>>>

Prey assimilation (feeding) rate

@@

C-mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}

@@

Maintenance rate of host biomass

@@

Maintenance rate of symbiont biomass

@@

Proportion N turnover recycled in host

@@

Proportion host metabolic CO\textsubscript{2} recycled to photosynthesis

@@

Proportion N turnover recycled in symbiont

@@

Proportion symbiont metabolic CO\textsubscript{2} recycled to
photosynthesis

@@

Maximum prey assimilation rate from host feeding

@@

Half-saturation constant for prey assimilation

@@

Maximum host DIN uptake rate

@@

Half-saturation constant for host DIN uptake

@@

Efficacy of CO\textsubscript{2} delivery to photosynthesis by host CCMs

@@

This flux, \(j_{eC}\), is assumed to be available to the host as a
respiratory substrate to support energetically-demanding processes; of
particular importance is the host's active carbon concentrating
mechanisms (CCMs) that supply CO\textsubscript{2} for symbiont
photosynthesis (Wooldridge 2013; Hopkinson, Tansik, and Fitt 2015). We
therefore specify \(j_{CO_2}\) as the host-mediated delivery of
CO\textsubscript{2} to photosynthesis that encompasses potentially
diverse CCMs, including active transport of bicarbonate, carbonic
anhydrase-catalyzed conversion of bicarbonate to CO\textsubscript{2} to
promote diffusion toward the symbiont (Tansik, Fitt, and Hopkinson
2015), and acidification of the symbiosome to increase localized
CO\textsubscript{2} concentrations around the symbiont (Barott et al.
2014). Since these active CCMs require energetic input by the host, we
define \(j_{CO_2}\) as proportional to \(j_{eC}\), assuming that some of
this carbon is respired to energize the CCMs. This formulation means
that the symbiont indirectly ensures its own CO\textsubscript{2} supply
by providing fixed carbon (=energy) to the host (Wooldridge 2013). The
parameter \(k_{CO_2}\) scales the efficacy of host CCMs, which enables
the comparison of different rates of CO\textsubscript{2} delivery that
may characterize different coral species (Wooldridge 2014a). The active
input of CO\textsubscript{2} to the photosynthesis SU is therefore
specified as:
